### 2013-06-25 inst/examples/sensitivity.Rmd
ready for runs on zero

```{r parallel}
require(snowfall)
sfInit(parallel=TRUE, cpu=8)
sfLibrary("nonparametric-bayes")
sfExportAll()
```

@@

```{r}
yields <- melt(yields, id=c("method", "V1", "sd"))
ggplot(yields) + geom_histogram(aes(V1)) + facet_wrap(~method, scale='free')
yields
````

>>>>

```{r parallel}
require(snowfall)
sfInit(parallel=TRUE, cpu=8)
sfLibrary(nonparametricbayes)
sfExportAll()
```

@@

```{r}
yields
#yields <- melt(yields, id=c("method", "V1", "sd"))
#ggplot(yields) + geom_histogram(aes(V1)) + facet_wrap(~method, scale='free')
````
